Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-19 manuscript.Rmd
figured out outliers
fixed x-axis on timeline plot

```{r setup, include = FALSE}
library(papaja)
library(knitr)
library(patchwork)
library(scales)
library(ggforce)
library(tidyverse)
library(rstatix)
```

@@

@@

timelines <- function(ds) {
  ggplot(ds, aes(x = clock_time_start, y = prop, fill = Position)) + 
  geom_bar(stat = "identity") + 
  facet_wrap("id_uni",ncol = 1, strip.position = "left") + 
  scale_fill_manual(values = c("Nap" = "gray",pal)) + 
  scale_x_time(breaks = breaks_width("2 hour"), name = "", minor_breaks = waiver()) + 
  theme(legend.position = "bottom", 
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 10, color = "black", angle = 315, hjust = -.15),
        strip.background = element_blank(),
        strip.text.y = element_blank()) + ylab("")
}

>>>>

```{r setup, include = FALSE}
library(papaja)
library(knitr)
library(patchwork)
library(scales)
library(ggforce)
library(hms)
library(tidyverse)
library(rstatix)
```

@@

#Worst three Kappa individuals are 9, 111-4, and 120-2
#Worst three Kappa groups are 9, 110-4
#Worst three Overall Accuracy (grouped) are 104-1, 106-1, 108-2 (first two are pt 2 outliers)

@@

timelines <- function(ds) {
  lims <- as_hms(c('09:00:00', '21:59:00'))
  breaks = as_hms(c('09:00:00', '10:00:00', '11:00:00', '12:00:00', '13:00:00', '14:00:00', '15:00:00', '16:00:00', '17:00:00', '18:00:00', '19:00:00', '20:00:00', '21:00:00'))
  ggplot(ds, aes(x = clock_time_start, y = prop, fill = Position)) + 
  geom_bar(stat = "identity") + 
  facet_wrap("id_uni",ncol = 1, strip.position = "left") + 
  scale_fill_manual(values = c("Nap" = "gray",pal)) + 
  scale_x_time(breaks = breaks_width("4 hour"), name = "", limits = lims) + 
  theme(legend.position = "bottom", 
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(size = 10, color = "black"),
        strip.background = element_blank(),
        strip.text.y = element_blank()) + ylab("")
}
